### 2015-05-26 writing/SNLI paper/corpus.tex
Lots of paper cleanup.

\subsection{Motivation}

To date, the primary sources of annotated NLI corpora have been the
Recognizing Textual Entailment (RTE)
tasks.\footnote{\url{http://aclweb.org/aclwiki/index.php?title=Textual_Entailment_Resource_Pool}}
These are generally high-quality, hand-labeled data sets, and they
have stimulated innovative logical and statistical models of natural
language reasoning, but their small size limits their utility as a
testbed for distributed representations. The recent SemEval 2014 data
set called Sentences Involving Compositional Knowledge (SICK) is a
step up in terms of size, but only to about 10,000 examples, and its
partly automatic construction introduced some spurious patterns into
the data (\citealt{marelli2014semeval}, $\S$6). Finally, the
Denotation Graph data set \cite{hodoshimage} contains millions of
examples, but it was constructed using fully automatic methods, and is
noisy enough that it is probably suitable only as a source of
supplementary training data.

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label \cite{marelli2014sick}. For
instance, the sentence pair \word{A boat sank in the Pacific
  ocean} and \word{A boat sank in the ocean} could reasonably in
numerous ways depending on how the objects and events are grounded. If
the two boats are different, then the sentences are semantically
independent. If the boats are the same and the oceans are the same,
then the first sentence entails the second (in the relevant
commonsense way). If the boats are the same and the oceans are
different, then the two events are (commonsense) contradictory. This
kind of indeterminacy can be resolved only once the questions of
coreference are resolved.

@@

For the premises, we used the Flickr30k corpus \cite{hodoshimage}, a collection of approximately 160k captions from that corpus (corresponding to about 30k images) collected in an earlier crowdsourced effort. The captions were not authored by the photographers who took the source images, they tend to contain relatively literal scene descriptions that are suited to our approach, rather than those typically associated with personal photographs (as in their example: \textit{``Our trip to the Olympic Peninsula''}). We presented each caption to at least one worker, and some to more than one. With the exception of a handful that were flagged by workers as excessively difficult, at least three labeled pairs are available for each caption.

@@

\begin{figure}
\footnotesize
We will show you the caption for a photo. We will not show you the photo. Using only the caption and what you know about the world:
\begin{itemize}
\item Write one alternate caption that is \textbf{definitely} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that \textbf{might be} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that is \textbf{definitely} a \textbf{false} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors." This is different from the maybe correct category because its impossible for the dogs to be both running and sitting.}
\end{itemize}
\todo{Fix the broken examples here (SB)}
\caption{\label{instructions-1}The instructions used on Mechanical Turk for data collection.}
\end{figure}

@@

This validation phase is not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ. Though we used a very restrictive qualification (based on past approval rate) to select workers, we nonetheless discovered and deleted some instances of random guessing during an early round of validation, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.

For each pair that we validated, we chose a gold label. If any one of the three labels was chosen by at least three of the five annotators, that label is the gold label. If there was no such consensus, which occurred in about 0.2\% of cases, we chose the label `-'. While these unlabeled examples are included in the corpus distribution, they are unlikely to be helpful for the core classification task of NLI, and we do not include them when training and evaluating the models discussed in later sections. The results of this validation process are summarized in Tables \ref{validation-stats} and \ref{validation-freq}, and suggest that while fundamental limits of both our crowdsourcing methods and the task itself impose an upper bound on the consistency of our labels, the data is sufficiently high quality to pose a challenging but realistic machine learning task.

\subsection{The distributed corpus}
\todo{Update all statistics to reflect the latest relase candidate.}

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{6cm}p{0.75cm}p{1.4cm}p{6cm}}
  \toprule
A man inspects the uniform of a figure in some East Asian country. & \b{contr.}& \t{$\{$c c c c c$\}$} & The man is sleeping\\
\rule{0pt}{3ex}An older and younger man smiling. & \b{neut.}& \t{$\{$n n e n n$\}$} & Two men are smiling and laughing at the cats playing on the floor.\\
\rule{0pt}{3ex}A black race car starts up in front of a crowd of people. & \b{contr.}& \t{$\{$c c c c c$\}$} & A man is driving down a lonely road.\\
\rule{0pt}{3ex}A soccer game with multiple males playing. & \b{ent.}& \t{$\{$e e e e e$\}$} & Some men are playing a sport.\\
\rule{0pt}{3ex}A smiling costumed woman is holding an umbrella. & \b{neut.}& \t{$\{$n n e c n$\}$} & A happy woman in a fairy costume holds an umbrella.\\
    \bottomrule
% From 1.0rc3
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from the SNLI development set, shown with the gold labels and the full set of annotator labels (abbreviated).}
\end{table*}

Table~\ref{snli-examples} shows a set of randomly chosen validated examples from the development sent with their labels. Qualitatively, we find the data that we collected to draw fairly extensively on commonsense knowledge, suggesting that superficial word alignment models are unlikely to be able to succeed at classification. We find the sentences that we collected be largely fluent, correctly spelled English, with a mix of full sentences and bare noun phrases of a style that is appropriate for the underlying caption task. Punctution and capitalization are only intermittently presE

@@

The distributed corpus includes parses for every sentence produced by the Stanford PCFG Parser \cite{klein2003accurate}, both in the standard PTB format and in the binarized unlabeled format used by tree-structured neural network models, as in \S\ref{sentence-embedding}.

\todo{Update and expand (CM, SB)}

>>>>

To date, the primary sources of annotated NLI corpora have been the
Recognizing Textual Entailment (RTE)
tasks.\footnote{\url{http://aclweb.org/aclwiki/index.php?title=Textual_Entailment_Resource_Pool}}
These are generally high-quality, hand-labeled data sets, and they
have stimulated innovative logical and statistical models of natural
language reasoning, but their small size of a few hundred examples each
limits their utility as a testbed for learned distributed representations. 
The data for the SemEval 2014 task called Sentences Involving Compositional Knowledge (SICK) is a
step up in terms of size, but only to 4,500 training examples, and its
partly automatic construction introduced some spurious patterns into
the data (\citealt{marelli2014semeval}, $\S$6). Finally, the
Denotation Graph entailment set \cite{hodoshimage} contains millions of
examples of entailments between sentences and artificially constructed
short phrases, but it was labeled using fully automatic methods, and is
noisy enough that it is probably suitable only as a source of
supplementary training data.
\todo{also cf. PPDB?}

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label \cite{marelli2014sick}. For
instance, the sentence pair \word{A boat sank in the Pacific
  ocean} and \word{A boat sank in the ocean} could reasonably be labeled in
numerous ways depending on how the objects and events are grounded. If
the two boats are assumed to be different, then the sentences are semantically
independent. If the boats and the oceans are assumed to be the same,
then the first sentence entails the second (in the relevant
commonsense way). If the boats are assumed to be the same and 
\ii{the ocean} in the second sentence is interpreted with a specific referent 
that is not the Pacific, then the two events are (commonsense) contradictory. This
kind of indeterminacy can be resolved only once the questions of
coreference are resolved.

@@

For the premises, we used the Flickr30k corpus \cite{hodoshimage}, a collection of approximately 160k captions  (corresponding to about 30k images) collected in an earlier crowdsourced effort. The captions were not authored by the photographers who took the source images, they tend to contain relatively literal scene descriptions that are suited to our approach, rather than those typically associated with personal photographs (as in their example: \textit{Our trip to the Olympic Peninsula}). We presented each caption to at least one worker, and some to more than one. With the exception of a handful that were flagged by workers as excessively difficult, at least three labeled pairs are available for each caption.

@@

\begin{figure}
\begin{framed}
\small
We will show you the caption for a photo. We will not show you the photo. Using only the caption and what you know about the world:
\begin{itemize}
\item Write one alternate caption that is \textbf{definitely} a \textbf{true} description of the photo. \ii{Example: For the caption ``\ii{Two dogs are running through a field.}'' you could write ``\ii{There are animals outdoors.}"}
\item Write one alternate caption that \textbf{might be} a \textbf{true} description of the photo. \ii{Example: For the caption ``\ii{Two dogs are running through a field.}" you could write ``\ii{Some puppies are running to catch a stick.}"}
\item Write one alternate caption that is \textbf{definitely} a \textbf{false} description of the photo. \ii{Example: For the caption ``\ii{Two dogs are running through a field.}" you could write ``\ii{The pets are sitting on a couch.}" This is different from the maybe correct category because it's impossible for the dogs to be both running and sitting.}
\end{itemize}
\end{framed}

\caption{\label{instructions-1}The instructions used on Mechanical Turk for data collection.}
\end{figure}

@@

This validation phase is not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we present workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original composer of the pair. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ. Though we used a very restrictive qualification (based on past approval rate) to select workers, we nonetheless discovered and deleted some instances of random guessing during an early round of validation, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.
\todo{Leave in mention of qual?}

For each pair that we validated, we chose a gold label. If any one of the three labels was chosen by at least three of the five annotators, that label is the gold label. If there was no such consensus, which occurred in about 0.2\% of cases, we chose the label `-'. While these unlabeled examples are included in the corpus distribution, they are unlikely to be helpful for the standard NLI classification task, and we do not include them when training and evaluating the models discussed in later sections. The results of this validation process are summarized in Tables \ref{validation-stats} and \ref{validation-freq}, and suggest that while fundamental limits of both our crowdsourcing methods and the task itself impose an upper bound on the consistency of our labels, the data is sufficiently high quality to pose a challenging but realistic machine learning task.

\subsection{The distributed corpus}

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{6cm}p{0.75cm}p{1.4cm}p{6cm}}
  \toprule
A man inspects the uniform of a figure in some East Asian country. & \b{contr.}& \t{$\{$c c c c c$\}$} & The man is sleeping\\
\rule{0pt}{3ex}An older and younger man smiling. & \b{neut.}& \t{$\{$n n e n n$\}$} & Two men are smiling and laughing at the cats playing on the floor.\\
\rule{0pt}{3ex}A black race car starts up in front of a crowd of people. & \b{contr.}& \t{$\{$c c c c c$\}$} & A man is driving down a lonely road.\\
\rule{0pt}{3ex}A soccer game with multiple males playing. & \b{ent.}& \t{$\{$e e e e e$\}$} & Some men are playing a sport.\\
\rule{0pt}{3ex}A smiling costumed woman is holding an umbrella. & \b{neut.}& \t{$\{$n n e c n$\}$} & A happy woman in a fairy costume holds an umbrella.\\
    \bottomrule
% From 1.0rc3
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from the SNLI development set, shown with the gold labels and the full set of annotator labels (abbreviated). Unlike in many existing NLI corpora, the premise and hypothesis sentences in SNLI are often too dissimilar in structure to support approaches to NLI that rely on building sentence-to-sentence alignments.}
\end{table*}

Table~\ref{snli-examples} shows a set of randomly chosen validated examples from the development sent with their labels. Qualitatively, we find the data that we collected to draw fairly extensively on commonsense knowledge, suggesting that superficial word alignment models are unlikely to be able to succeed at classification. We find the sentences that we collected be largely fluent, correctly spelled English, with a mix of full sentences and caption-style noun phrase fragments. Punctution and capitalization are only intermittently present.

@@

The distributed corpus includes parses for every sentence produced by the Stanford PCFG Parser \cite{klein2003accurate} (trained on the standard training set as well as on the Brown Corpus; \citealt{francis1979brown}), both in the standard PTB format and in the binarized unlabeled format used by tree-structured neural network models, as in \S\ref{sentence-embedding}.

\todo{Update as appropriate (CM)}

### 2015-05-26 writing/SNLI paper/entailment_eval.tex
Paper update.
Add PDF of learning curve
Misc, including rc3 stats.
Add numbers for the lexical baseline classifier
Assorted updates, new paper stats
Paper update
Updating paper to match details of rc3.
Lots of paper cleanup.

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{SNLI}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{68.0} & \t{38.7} & \t{49.3} & \t{73.5} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
For comparision, results are also reported on the RTE-3 dataset.
\todo{numbers are approx.}
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

%
% BOW RESULTS TABLE
%
% Some definitions
\def\t#1{\small{#1}}
\def\b#1{\t{\textbf{#1}}}
\def\colspaceS{2.0mm}
\def\colspaceM{3.0mm}
\def\colspaceL{4.0mm}

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{2-Class}} & \b{3-Class} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & \t{77.3} \\
\t{Unigrams Only}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\t{Unlexicalized}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the 2-class and 3-class SNLI dataset, as well as precision/recall
  on the 2-class task to allow for comparision with the RTE systems.
Ablation studies are reported for removing bigram features and all lexical
  features.
\todo{numbers are approx.}
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Commenting out until PDF available. -S
%\Fig{learning_curves_bow.pdf}{0.6}{bowlearncurve}{
%A learning curve for the lexicalized and unlexicalized baseline classifiers.
%Note the y axis starting at a random-chance accuracy of 33\%.
%\todo{numbers are approx.}
%}

@@

The word embeddings for all of the moedels are initialized the 200d reference GloVe vectors \cite{pennington2014glove} and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 200d embeddings into the 50d working space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{Sum of words}            & \t{} & \t{} \\
\t{RNN}            & \t{} & \t{} \\
\t{LSTM RNN}            & \t{75?} & \t{72?} \\
\t{TreeRNN}            & \t{} & \t{} \\
\t{TreeRNTN}            & \t{58?} & \t{56?} \\
\t{LSTM TreeRNN}            & \t{72?} & \t{69?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers}
}
\end{table}

>>>>

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{SNLI}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{68.0} & \t{38.7} & \t{49.3} & \t{73.5} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
For comparision, results are also reported on the RTE-3 dataset.
\todo{numbers are still dev.}
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

%
% BOW RESULTS TABLE
%

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceM}c}
\hline
\textbf{System} & \b{Dev} & \multicolumn{4}{c}{\b{Test}} \\
 & \t{Acc.} & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{79.4} & \t{82.3} & \t{80.9} & \t{78.2} \\
\t{Unigrams Only}          & \t{??.?} & \t{71.1} & \t{77.7} & \t{74.3} & \t{71.6} \\
\t{Unlexicalized}          & \t{??.?} & \t{56.0} & \t{64.4} & \t{59.9} & \t{50.39} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the 2-class and 3-class SNLI dataset, as well as precision/recall
  on the 2-class task to allow for comparision with the RTE systems.
Ablation results are reported for models lacking bigram features and lacking all lexical
  features.
\todo{fill in dev numbers}
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Commenting out until PDF available. -S
% Running 'make' should generate PDF from gnuplot
\Fig{learning_curves_bow.pdf}{0.6}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers,
plotted on a log scale.
Note the y axis starting at a random-chance accuracy of 33\%.
\todo{numbers are approx.}
}

@@

The word embeddings for all of the moedels are initialized the 300d reference GloVe vectors \cite{pennington2014glove} and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensianal phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{?} & \t{68} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers}
}
\end{table}

### 2015-05-26 writing/SNLI paper/intro.tex
Lots of paper cleanup.

NLI has been addressed using a wide variety of techniques, including
those grounded in syntactic structures, knowledge bases, and symbolic
logic. In recent years, it has become an important testing ground for
approaches employing \emph{distributed} word and phrase
representations. Distributed representations excel at capturing
relations based in similarity, and they have proven effective at
modeling simple dimensions of meaning like evaluative sentiment
\cite{socher2013acl1}, but it is less clear that they can be
trained to support the full range of logical inferences required for
NLI. In the SemEval 2014 task aimed at evaluating distributed
representations for NLI, the best-performing systems relied heavily on
additional features and reasoning capabilities
\cite{marelli2014semeval}.

@@

To address this, we present a new corpus of sentence pairs labeled for
entailment, contradiction, and semantic independence. At 550,152
sentence-pairs, this corpus is orders of magnitude larger than all
other resources of its type. And, in contrast to many such resources,
all of the sentences were written by humans in a grounded,
naturalistic context. In a separate validation phase, we collected
four additional judgments for each label for 56,941 of the examples,
and 98\% of cases emerge with a gold label, which attests to the high
quality of the data.

@@

>>>>

NLI has been addressed using a wide variety of techniques, including
those grounded in syntactic structures, knowledge bases, and symbolic
logic. In recent years, it has become an important testing ground for
approaches employing \emph{distributed} word and phrase
representations. Distributed representations excel at capturing
relations based in similarity, and they have proven effective at
modeling simple dimensions of meaning like evaluative sentiment
\cite{socher2013acl1}, but it is less clear that they can be
trained to support the full range of logical and commonsense
 inferences required for NLI. In the SemEval 2014 task aimed at evaluating distributed
representations for NLI, the best-performing systems relied heavily on
additional features and reasoning capabilities
\cite{marelli2014semeval}.

@@

To address this, we present a new corpus of sentence pairs labeled for
entailment, contradiction, and semantic independence. At 570,152
sentence-pairs, this corpus is orders of magnitude larger than all
other resources of its type. And, in contrast to many such resources,
all of the sentences were written by humans in a grounded,
naturalistic context. In a separate validation phase, we collected
four additional judgments for each label for 56,941 of the examples.
Of these, 98\% of cases emerge with a three annotator consensus, 
and 58\% see a unanimous consensus from all five annotators, 
which attests to the high quality of the data.

@@

\todo{Plain LSTMs strong, used in transfer.}
